An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-04-11 EconGrowth.Rnw
Added non-energy CES models for all countries.

modelUS <- cesModel("US")
print(summary(modelUS))

>>>>

print("US")
print(summary(cesModel("US")))
print("UK")
print(summary(cesModel("UK")))
print("JP")
print(summary(cesModel("JP")))
print("CN")
print(summary(cesModel("CN")))
print("ZA")
print(summary(cesModel("ZA")))
print("SA")
print(summary(cesModel("SA")))
print("IR")
print(summary(cesModel("IR")))
print("TZ")
print(summary(cesModel("TZ")))
print("ZM")
print(summary(cesModel("ZM")))
